EWJN from a BCS Superconductor

### 2021-02-05 paper.tex
Adds additional figures including cliffedge and scripts for nam and lindhard noise calculations

>>>>

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{HighTempNam1}
	\caption{$T_1(z)$ at various temperatures, with $T_1$ in nanoseconds and $z$ in micrometers for parameters described in the text.} \label{fig:HighTempNam1}
\end{figure}
\Cref{fig:HighTempNam1} shows the result of these approximations, plotting the relaxation time $T_1$ at increasing distances away from the qubit.
In that figure, $\omega = \SI{1e9}{\per\second}$, $\omega_p = \SI{3.5e15}{\per\second}$, $\tau = \SI{1e-14}{\second}$, $\vf = \SI{1e6}{\m\per\s}$, $T_c = \SI{1e11}{\per\s}$, $d = \SI{8.4e-30}{\coulomb\m}$, and the temperatures are given in the legend in units of $T_c$.
Of note is how the noise calculated for the superconducting case goes to the normal state as $T \rightarrow T_c$, as well as how little the normal state depends on the temperature.
Also of note is the very large increase in the relaxation time for $T = .9 T_c$.
This reflects the situation where $\Delta$ is high enough that fluctuations with frequency $\omega$ can no longer excite states in the superconductor.
\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{namNoiseCliff}
	\caption{$\chi = \frac{1}{T_1(z)}$ for fixed $z$, but varying $\omega$ and $\Delta$} \label{fig:Cliff}
\end{figure}
This is plotted in \cref{fig:Cliff}, which shows the cliff-edge along which $\omega$ is sufficiently smaller than $\Delta$.
In this regime, Johnson noise no longer becomes an issue for these qubits.
